---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Mouse preimplantation embryo data from Deng et al, 2014


## Description

1. This R package stores [Deng et al.](http://science.sciencemag.org/content/343/6167/193.full)(2014) data directly downloaed from National Center for Biotechnology Information Gene Expression Omnibus (['GSE45719'](https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE45719)).
2. See [Deng et al.](http://science.sciencemag.org/content/343/6167/193.full)(2014) for data processing details. Briefly, the count table includes single cell samples after quality filtering and before normalization. 
3. [Hicks et al.](http://www.biorxiv.org/content/early/2015/08/25/025528)(2015) provides a concise summary of the experimental design in [Deng et al.](http://science.sciencemag.org/content/343/6167/193.full)(2014) (and many other single cell RNA-seq studies).


## How to cite

If you use the data, please cite:

> Qiaolin Deng, Daniel Ramskold, Bjorn Reinius, and Richard Sandberg. *Single-cell RNA-seq reveals dynamic, random monoallelic gene expression in mammalian cells.* Science 343(6167), 193-6 (2014) DOI: 10.1126/science.1245316


## Installation
To install, run in R:

```{r, eval = FALSE}
install.packages("devtools")
devtools::install_github("jhsiao999/singleCellRNASeqMouseDengESC")
```


